Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-31 WSSSPE3/report/WSSSPE3_review.tex
adding ref/cite for Ahalt lightning talk

\item \textbf{Stan Ahalt, Bruce Berriman, Maxine Brown, Jeffrey Carver, Neil
Chue Hong, Allison Fish, Ray Idaszak, Greg Newman, Dhabaleswar Panda, Abani
Patra, Elbridge Gerry Puckett, Chris Roland, Douglas Thain, Selcuk Uluagac, and
Bo Zhang: \textit{Scientific Software Success: Developing Metrics While
Developing Community}}. The effort behind this talk given by Ray Idaszak started
from a breakout group at an NSF SI2 workshop in 2015, and centers around
building a framework for creating metrics for scientific software. This
framework would improve both the metrics and the software it evaluates, and
could also serve as a tool for building a community around the idea. With
especially the last-mentioned idea (building a community) in mind, a software
``peer review group'' would be created, representing stakeholders who will
self-review software created by their respective communities, and will
concurrently develop metrics. The whole project should be community-governed,
without a single institution overseeing the activities or infrastructure, with
the hope to evolving community-generated and adopted standards. The generation
of metrics would be tied to the actual evaluation of software, creating an
incentive by improving the evaluated software itself during this process. The
framework code would provide infrastructure for the creation of metrics and
evaluation, and forums for generation of software success metrics. It would also
support code reviews of the evaluated software. An open question is whether it
is possible to fit the resulting metrics in a common template. So far, this is
still in a design phase, with a white paper at the CSESSP workshop 2015 and this
talk, but the WSSSPE workshops are seen as a forum for the community to assemble
and act, and is planned to be used also in the future to build this community
and framework.

>>>>

\item \textbf{Stan Ahalt, Bruce Berriman, Maxine Brown, Jeffrey Carver, Neil
Chue Hong, Allison Fish, Ray Idaszak, Greg Newman, Dhabaleswar Panda, Abani
Patra, Elbridge Gerry Puckett, Chris Roland, Douglas Thain, Selcuk Uluagac, and
Bo Zhang: \textit{Scientific Software Success: Developing Metrics While
Developing Community}}. The effort behind this talk given by Ray Idaszak started
from a breakout group at an NSF SI2 workshop in 2015, and centers around
building a framework for creating metrics for scientific software~\cite{ahalt-csessp}. This
framework would improve both the metrics and the software it evaluates, and
could also serve as a tool for building a community around the idea. With
especially the last-mentioned idea (building a community) in mind, a software
``peer review group'' would be created, representing stakeholders who will
self-review software created by their respective communities, and will
concurrently develop metrics. The whole project should be community-governed,
without a single institution overseeing the activities or infrastructure, with
the hope to evolving community-generated and adopted standards. The generation
of metrics would be tied to the actual evaluation of software, creating an
incentive by improving the evaluated software itself during this process. The
framework code would provide infrastructure for the creation of metrics and
evaluation, and forums for generation of software success metrics. It would also
support code reviews of the evaluated software. An open question is whether it
is possible to fit the resulting metrics in a common template. So far, this is
still in a design phase, with a white paper at the CSESSP workshop 2015 and this
talk, but the WSSSPE workshops are seen as a forum for the community to assemble
and act, and is planned to be used also in the future to build this community
and framework.
